Why Real-World Subgraph Isomorphism is Easy, \\ and What This Means for Graph Databases

### 2016-10-22 paper/paper.tex
Another one

The filter / verify paradigm also influences other research. For example, recently
\citet{DBLP:journals/pvldb/YuanMG13} continue a line of supergraph search work, again using a
filtering step to avoid subgraph isomorphism calls. There is also research into maintaining indices
when the set of target graph changes: for example \citet{DBLP:conf/sigmod/YuanMYG15} look at
algorithms for updating graph indices. And in describing a system for reusing results of queries
which are sub- or super-graphs of previous queries, \citet{DBLP:conf/edbt/WangNT16} state that
querying is a ``very costly operation as it entails the \NP-complete problem of subgraph
isomorphism'', and place ``an emphasis on the number of unnecessary subgraph isomorphism tests''.

>>>>

The filter / verify paradigm also influences other research. For example, recently
\citet{DBLP:journals/pvldb/YuanMG13} continue a line of supergraph search work, again using a
filtering step to avoid subgraph isomorphism calls.  \citet{DBLP:journals/tkde/HongZLY15} look at
graph database subgraph matching with an additional set similarity constraint, and state that
Ullmann's algorithm and VF2 are ``usually costly for large graphs'' because they ``do not utilize
any index structure''. They propose an indexing structure, which takes over 2,000 seconds to
construct, and uses nearly 2GBytes of space.  There is also research into maintaining indices when
the set of target graph changes: for example \citet{DBLP:conf/sigmod/YuanMYG15} look at algorithms
for updating graph indices. And in describing a system for reusing results of queries which are sub-
or super-graphs of previous queries, \citet{DBLP:conf/edbt/WangNT16} state that querying is a ``very
costly operation as it entails the \NP-complete problem of subgraph isomorphism'', and place ``an
emphasis on the number of unnecessary subgraph isomorphism tests''.
